---
title: "Untitled"
output: html_document
date: "`r Sys.Date()`"
---

```{r}
library(tidyverse)
library(tidygraph)
library(ggraph)
```

1. [Movie Genres] How do movie genres relate to one another? Is romance + comedy
a more common combination than fantasy + adventure? We will use the dataset
[here](https://github.com/krisrs1128/stat436_s24/raw/main/data/movie_links.csv)
to answer these questions, using a node-link diagram inspired by (but much
simpler than) the [film
flowers](https://observablehq.com/@sxywu/introduction-to-svg-and-d3-js) project
by Shirley Wu.

    a. Build a `tbl_graph` containing the movies and their links.
    
    b. Create a node-link diagram to represent the connections between movies and
    their genres.
    
    c. A list of all the genres in this network is available
    [here](https://github.com/krisrs1128/stat992_f23/blob/main/activities/week9/genres.csv).
    Design a strategy to distinguish between genres and movies, and justify your
    choice of visual encodings. _Hint: Mutate the nodes in the `tbl_graph`._

```{r}
edges <- read_csv("https://github.com/krisrs1128/stat436_s24/raw/main/data/movie_links.csv")
genres <- read_csv("https://github.com/krisrs1128/stat436_s24/raw/main/data/genres.csv")

G <- tbl_graph(edges = edges) %N>%
  mutate(type = name %in% genres$genre)

ggraph(G, "kk") +
  geom_edge_link(colour = "#d3d3d3", width = 0.5, alpha = 0.6) +
  geom_node_text(aes(label = name, size = type, col = type)) +
  scale_color_manual(values = c("#BF4545", "#225C73")) +
  scale_size_discrete(range = c(2.5, 5)) +
  theme_void() +
  theme(legend.position = "none")

ggraph(G, "matrix") +
  geom_edge_tile(mirror = TRUE) +
  geom_node_text(aes(label = name, col = type), x = -.5, hjust = 1) +
  geom_node_text(aes(label = name, col = type), y = -0.5, angle = 90, hjust = 1) +
  scale_x_discrete(expand = c(0, 200, 0, 0)) +
  scale_y_discrete(expand = c(0, 200, 0, 0)) +
  coord_fixed()
```

1. [Climate Crisis Youtube recommendations] We will study a
[dataset](https://observablehq.com/@emma-ba/youtube-recommendation-network-on-the-climate-crisis)
giving links between Youtube videos related to the climate crisis.  The data
were gathered by simulating a user browsing through recommendations, after
having initially searched using a set of climate-related seed terms. Each node
is a video, which includes features like the number of views and the channel it
belongs to. Each edge provides an algorithmically generated recommendation.

a. Build a `tbl_graph` from the provided [node](https://github.com/krisrs1128/stat992_f23/raw/main/activities/week9/climate-nodes.csv) and [edge](https://github.com/krisrs1128/stat992_f23/raw/main/activities/week9/climate-edges.csv) data.

b. Visualize the connections between videos as a node-link diagram. Color nodes in by the simulated browser session.

c. Visualize the connections between videos as an adjacency matrix.

d. Compare and contrast the visualizations in parts (b) and (c). What are
some of the trade-offs associated with using one view vs. the other?

e. Select a small number of channels of interest (e.g., "The Daily Show with
Trevor Noah") For either parts (b) or (c), find a way to visually
distinguish nodes belonging to these channels from the rest.


```{r}
nodes <- read_csv("https://github.com/krisrs1128/stat436_s25/raw/main/data/climate-nodes.csv")
edges <- read_csv("https://github.com/krisrs1128/stat436_s25/raw/main/data/climate-edges.csv")
G <- tbl_graph(nodes, edges)
G <- G |>
  mutate(session_group = fct_lump_n(session, n = 6))

# how many from each session?
nodes |>
  count(session) |>
  arrange(-n)

# node-link diagram
ggraph(G) +
  geom_edge_link(edge_color = "#d5d5d5", edge_width = 0.4) +
  geom_node_point(aes(col = session_group)) +
  scale_color_brewer(palette = "Set2") +
  theme_void()
```

```{r}
# adjacency matrix view
ggraph(G, layout = "matrix") +
  geom_edge_tile(edge_color = "#d5d5d5", edge_width = 0.4, mirror = TRUE) +
  geom_node_point(aes(col = session_group), x = 0) +
  scale_color_brewer(palette = "Set2") +
  theme_void()
```

```{r}
# focusing on one channel
G_ <- G |>
  mutate(
    focus = ifelse(channel == "The Daily Show with Trevor Noah", "highlight", "other"),
    focus = ifelse(is.na(focus), "other", focus),
    focus = factor(focus, levels = c("other", "highlight"))
  )

ggraph(G_) +
  geom_edge_link(edge_color = "#d5d5d5", edge_width = 0.4) +
  geom_node_point(aes(col = session_group, alpha = focus, size = focus)) +
  scale_color_brewer(palette = "Set2") +
  scale_alpha_discrete(range = c(0.2, 1)) +
  theme_void()
```