---
title: "Untitled"
output: html_document
date: "`r Sys.Date()`"
---

```{r, echo = FALSE}
knitr::opts_chunk$set(warnings = FALSE, message = FALSE)
```

```{r}
library(tidyverse)
library(shiny)
library(DT) # for shiny's table
theme_set(theme_bw())
```

[Birds Brushed Scatterplot]. The
[`birds`](https://raw.githubusercontent.com/krisrs1128/stat479_s22/main/exercises/data/birds.csv)
and `bird_summaries` datasets defined below give characteristics of the eggs
laid by different species of birds. In this problem, you will build an
interactive app to compare egg `Asymmetry` and `Ellipticity` across species and
genera.

```{r}
birds <- read_csv("https://raw.githubusercontent.com/krisrs1128/stat479_s22/main/exercises/data/birds.csv") |>
    separate(Species, c("genus", "species2"))

bird_summaries <- birds |>
    group_by(genus) |>
    summarise(
    across(
        c("Asymmetry", "Ellipticity",
        "AvgLength (cm)", "Number of images",
        "Number of eggs"),
        list(
            MEAN = mean, 
            STANDARD_DEVIATION = sd)
        )
    ) |>
    arrange(-Ellipticity_MEAN)
```

a. Create a scatterplot of `Asymmetry` vs. `Ellipticity` which supports
brushing. Specifically, whenever the user brushes over a set of points in the
scatterplot, they should be shown a table of the selected species. Also,
change the color of the currently brushed points, so that they stand out more
clearly.

```{r}
scatter <- function(df, selected) {
    palette <- c("#d4d4d4", "black")
    df |>
        mutate(selected_ = selected) |>
        ggplot() +
        geom_point(aes(Asymmetry, Ellipticity, color = as.factor(selected_))) +
        scale_color_manual(values = palette)
}

ui <- fluidPage(
  titlePanel("Birds Brushed Scatterplot"),
  plotOutput("plot", brush = "scatter_brush"),
  DTOutput("table")
)
server <- function(input, output) {
    selected <- reactiveVal(rep(TRUE, nrow(birds)))
     observeEvent(
        input$scatter_brush, {
        brushed_points <- brushedPoints(birds, input$scatter_brush, allRows = TRUE)
        selected(brushed_points$selected_)
    }
  )
  output$plot <- renderPlot(scatter(birds, selected()))
  output$table <- renderDT(filter(birds, selected()))
}

shinyApp(ui, server)
```
