---
title: "Untitled"
output: html_document
date: "`r Sys.Date()`"
---

```{r, echo = FALSE}
knitr::opts_chunk$set(warnings = FALSE, message = FALSE)
```

```{r}
library(tidyverse)
th <- theme_minimal() + 
  theme(
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "#f7f7f7"),
    panel.border = element_rect(fill = NA, color = "#0c0c0c"),
    axis.text = element_text(size = 14),
    axis.title = element_text(size = 16),
    strip.text = element_text(size = 16),
    legend.position = "bottom"
  )
theme_set(th)
```
    
1. [Polio Clustering] The polio dataset contains weekly counts of new polio
cases across each state in the United States, starting as early as 1912. In this
question, our goal is to apply $K$-means to group states with similar incidence
patterns.

```{r}
polio <- read_csv("https://uwmadison.box.com/shared/static/nm7yku4y9q7ylvz5kbxya3ouj2njd0x6.csv")
head(polio)
```
  
a. Is it necessary to reshape the data before it can be used in the
`kmeans` function? If so, provide the code. If not, provide a brief
explanation.
  
```{r}
x <- polio |>
  pivot_wider(names_from = period_start_date, values_from = cases, values_fill = 0)
```

b. Let `x` contain the output from part (a). Compare the two
approaches to $K$-means in the code block below. Which would you recommend
using? Justify your choice.
  
  Option 1:
```{r, eval = FALSE}
x |>
  select(-state) |>
  kmeans(centers = 5)
```
          
  Option 2:

```{r, eval = FALSE}
x |>
  select(-state) |>
  scale() |>
  kmeans(centers = 5)
```
    
    Option 3:
    
```{r, eval = FALSE}
x |>
  select(-state) |>
  t() |>
  scale() |>
  t() |>
  kmeans(centers = 5)
```

c. Provide code needed for extracting and visualizing centroids
from the $K$-means fit made in part (b). Draw a rough sketch of the expected
result and include annotations that would help a reader understand the output.

We will normalize by state, as in Option 3.

```{r}
fit <- x |>
  select(-state) |>
  t() |>
  scale() |>
  t() |>
  kmeans(centers = 5)
```

This will visualize the cluster centroids.

```{r}
library(tidymodels)
x_clust <- augment(fit, x)
tidy(fit) |>
  pivot_longer(-any_of(c("size", "withinss", "cluster"))) |>
  mutate(name = as_date(name)) |>
  ggplot() +
    geom_point(aes(name, log(1 + value)), size = 0.4) +
    scale_y_continuous(expand = c(0, 0)) +
    facet_wrap(~ reorder(cluster, value), nrow = 3)
```

This groups the raw time series according to their cluster membership.

```{r}
library(scico)
x_clust |>
  pivot_longer(starts_with("19")) |>
  mutate(name = as_date(name)) |>
  ggplot() +
    geom_tile(aes(name, reorder(state, value), fill = log(1 + value), col = log(1 + value)), width = 7) +
    scale_fill_scico(palette = "berlin", midpoint = 3) +
    scale_color_scico(palette = "berlin", midpoint = 3) +
    scale_x_date(expand = c(0, 0)) +
    facet_grid(reorder(.cluster, -value) ~ ., scales = "free", space = 'free')
```