---
title: "Untitled"
output: html_document
date: "`r Sys.Date()`"
---

```{r, echo = FALSE}
knitr::opts_chunk$set(warnings = FALSE, message = FALSE)
```

```{r}
library(tidyverse)
library(tidygraph)
library(ggraph)
theme_set(theme_bw())
```

[COVID-19 Phylogeny] We will visualize a phylogenetic tree of [SARS-CoV-2
genetic sequences](https://observablehq.com/@mbostock/sars-cov-2-phylogenetic-tree).
Each sequence has been annotated with the date and location it was found, and we
will try to see how genetic variation covaries with these measurements.

a. Build a `tbl_graph` using the
[links](https://github.com/krisrs1128/stat436_s24/raw/main/data/covid-edges.csv)
and
[nodes](https://github.com/krisrs1128/stat436_s24/raw/main/data/covid-nodes.csv)
associated with the phylogenetic tree. Note that many nodes do not have
variables associated with them. This is because annotations are only
available for the leaves of the
tree, and nodes are unobserved common ancestor viruses.

```{r}
edges <- read_csv("https://github.com/krisrs1128/stat436_s24/raw/main/data/covid-edges.csv")
nodes <- read_csv("https://github.com/krisrs1128/stat436_s24/raw/main/data/covid-nodes.csv")


nodes
edges

G <- tbl_graph(nodes = nodes, edges = edges)
G

```

b. Visualize the phylogenetic tree using the data from (a).

```{r}
ggraph(G) +
    geom_edge_link() +
    geom_node_point()
    # node layer
    # links layer

ggraph(G) +
    geom_edge_diagonal() +
    geom_node_point()
```

c. Visually encode the date or location at which each sequence was found (for
a challenge, try encoding both). Justify your choice of encodings -- what are
some advantages / downsides of the approach you decided on?

```{r}
ggraph(G) +
    geom_edge_diagonal() +
    geom_node_point(aes(col = country))

# rnaturalearth

G |>
    activate(nodes) |>
    pull(country) |>
    table()

G |>
    activate(nodes) |>
    mutate(
        country_group = fct_lump_n(country, n = 7)
    ) |>
    pull(country_group) |>
    table()

G <- G |>
    activate(nodes) |>
    mutate(country_group = fct_lump_n(country, n = 7))

ggraph(G) +
    geom_edge_diagonal(edge_color = "#bebdbd") +
    geom_node_point(aes(col = country_group), size = 3) +
    facet_wrap(~ cut(date, 5))

```

d. Discuss the resulting visualization. For example, how much genetic
diversity do different countries have? Where are different waves located
genetically?