---
title: "Untitled"
output: html_document
date: "`r Sys.Date()`"
---

```{r}
knitr::opts_chunk$set(warnings = FALSE, message = FALSE)
library(tidyverse)
th <- theme_classic() +
    theme(
        axis.text = element_text(size = 14),
        legend.text = element_text(size = 14),
        axis.title = element_text(size = 20),
        legend.title = element_text(size = 20),
        strip.text = element_text(size = 20)
    )
theme_set(th)
```


[Plant Growth Experiment] This problem will give you practice with tidying a
dataset so that it can be easily visualized. The data describe the height of
several plants measured every 7 days. The plants have been treated with
different amounts of a growth stimulant. The first few rows are printed below --
`height.x` denotes the height of the plant on day `x`.

```{r}
library(tidyverse)
plants <- read_csv("https://uwmadison.box.com/shared/static/qg9gwk2ldjdtcmmmiropcunf34ddonya.csv")
plants
```

a. Propose an alternative arrangement of rows and columns that conforms to the
tidy data principle.

b. Implement your proposed arrangement from part (a).

```{r}
plants_long <- plants |>
    pivot_longer(starts_with("height"), names_to = "time_raw", values_to = "height") |>
    mutate(
        time = as.integer(str_extract(time_raw, "[0-9]+"))
    )

plants_long
ggplot(plants_long, aes(time, height, col = treatment)) +
    geom_line(aes(group = interaction(plantid, treatment))) +
    stat_smooth(method = "lm", se = FALSE, linewidth = 2) +
    facet_wrap(~ treatment)

plants_long |>
    arrange(plantid, treatment)
```

c. Using the dataset from (b), design and implement a visualization showing the
growth of the plants over time according to different treatments.

```{r}
plants_long
interaction(plants_long$plantid, plants_long$treatment)
```