---
title: "Untitled"
output: html_document
date: "`r Sys.Date()`"
---

```{r, echo = FALSE}
knitr::opts_chunk$set(warnings = FALSE, message = FALSE)
```

```{r}
library(sf)
library(tmap)
library(tidyverse)
library(ceramic)

# code to set a clean theme
th <- theme_minimal() + 
  theme(
    panel.grid.minor = element_blank(),
    panel.background = element_rect(fill = "#F7F7F7"),
    panel.border = element_rect(fill = NA, color = "#0c0c0c", size = 0.6),
    axis.text = element_text(size = 14),
    axis.title = element_text(size = 16),
    legend.position = "bottom"
  )
theme_set(th)
```

[Glacial Lakes]. The data at this [link](https://raw.githubusercontent.com/krisrs1128/stat436_s23/main/data/GL_3basins_2015.topojson) contain labels of glacial lakes the
Hindu Kush Himalaya, created during an ecological survey in 2015 by the
International Centre for Integrated Mountain Development.

```{r}
lakes <- read_sf("https://raw.githubusercontent.com/krisrs1128/stat436_s23/main/data/GL_3basins_2015.topojson") |>
  mutate(log_area = log(Area))

cols <- c("#023859", "#99ADBF")
```

a. How many lakes are in this dataset? What are the latitude / longitude
coordinates of the largest lakes in each Sub-basin?


 number of lakes = 3609 = nrow(lakes)

```{r}
nrow(lakes)

lakes |>
  group_by(Sub_Basin) |>
  summarise(max(Area))


top_lakes <- lakes |>
  group_by(Sub_Basin) |>
  slice_max(Area)


slice_min

slice_head()
```

b. Plot the polygons associated with each of the lakes identified in step
(a). _Hint: You may find it useful to split lakes across panels using the
`tmap_facets` function. If you use this approach, make sure to include a
scale with `tm_scale_bar()`, so that it is clear that lakes have different
sizes.

tm_shape --> initialize with a dataset

tm_polygons --> analogous to ggplot geoms

tm_line

tm_rgb




```{r}
tm_shape(top_lakes) +
  tm_polygons()

tm_shape(lakes) +
  tm_polygons()


tm_shape(top_lakes) +
  tm_polygons()  +
  tm_facets("Sub_Basin") +
  tm_scale_bar()
```

c. Visualize all lakes with latitude between 28.2 and 28.4 and with
longitude between 85.8 and 86. Optionally, add a basemap associated with
each lake.

```{r}
lakes_subset <- lakes |>
  filter(Latitude < 28.4, Latitude > 28.2) |>
  filter(Longitude < 86, Longitude > 85.8)

tm_shape(lakes_subset) +
  tm_polygons()
````

```{r}
Sys.setenv(MAPBOX_API_KEY="pk.eyJ1Ijoia3Jpc3JzMTEyOCIsImEiOiJjbHRkc3d4ZmEwNzEzMmlxcmxnb3pzMGl5In0.XZxJ626iKEWq2ylMn7cfiw")
basemap <- cc_location(cbind(85.9, 28.3), buffer = 1e4)

tm_shape(basemap) +
  tm_rgb() +
  tm_shape(lakes_subset) +
  tm_polygons(col = cols[2])



basemap <- cc_location(cbind(-89.429753, 43.0772122), buffer = 1e3)
tm_shape(basemap) +
  tm_rgb()
```
